%-------------------------
% Resume in Latex
% Author
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,12pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{multicol}
\usepackage{float}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={},
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\vspace{41mm}
\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{ADITYA PANDEY} % Your Name
\newcommand{\course}{Bachelor of Technology} % Your Program
\newcommand{\roll}{22U03020} % Your Roll No.
\newcommand{\phone}{9140541879} % Your Phone Number
\newcommand{\emaila}{aditya12bone@gmail.com} %Email 1
% \newcommand{\emailb}{201113057@manit.ac.in} %Email 2

\begin{document}
\fontfamily{cmr}\selectfont

\parbox{\dimexpr\linewidth-2.8cm\relax}{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\Large \name} & {\raisebox{0.0\height}{\footnotesize \faPhone}\ +91-\phone}\\
  {Sch. No.: \roll} & \href{mailto:\emaila}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emaila}} \\
  \course &  \href{mailto:\emailb}{\raisebox{0.0\height}{\footnotesize }\ {}}\\
  {Information Technology[IT]} &  \href{https://github.com/addy0328p}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {\color{blue}GitHub Profile}} \\
  {Indian Institute Of Information Technology, Bhopal} & \href{https://www.linkedin.com/in/aditya-pandey-5a2b7424a/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {\color{blue}LinkedIn Profile}}
\end{tabularx}
}

\section{\textbf{EDUCATIONAL DETAILS}}
 \begin{itemize}[leftmargin=0.01in, label={}, itemsep=4pt]
\resumeSubHeadingListStart
    \resumeSubheading
      { Indian Institute Of Information Technology, Bhopal, India}{CGPA/Percentage: 7.41[till 4th sem]}
      {B. Tech. - Computer Science Engineering}{2026}
    \resumeSubheading
       { Modern Academy, Lucknow }{CGPA/Percentage: 88.60}
      {ISC-12th }{2021}
    \resumeSubheading
      { Modern Academy, Lucknow }{CGPA/Percentage: 92.20}
      {ISC-10th }{2019}
  \resumeSubHeadingListEnd
\vspace{-3mm}

\section{\textbf{Technical Skills and Interests}}
 \begin{itemize}[leftmargin=0.05in, label={}, itemsep=10pt]
    \item {
     \textbf{Languages:} C/C++, JavaScript \\
     \textbf{Web Dev:} HTML, CSS, Tailwind, ReactJs, NodeJs, NestJs, FastAPI, MongoDB, ExpressJs \\
     \textbf{Devops Tools:} Git, GitHub \\
     \textbf{Tech Skills:} DSA, OOPs, DBMS, SQL \\
     \textbf{Areas of Interest:} Coding, Reading Books, Spirituality, Badminton
    }
 \end{itemize}
 \vspace{-10pt}

\section{\textbf{Personal Projects}}
\resumeSubHeadingListStart

\resumeProject
      { \href{https://addyhacke.github.io/Crest-site/}{{\color{blue}Crest Site:}} } %Project Name
      {An E-Commerce Beautiful Website.} %Project Name, Location Name
      {June, 2024} %Event Dates

      \resumeItemListStart
        \item {Tools \& technologies used: HTML, CSS, JavaScript}
        \item {Ensured a responsive and user-friendly design.}
    \resumeItemListEnd

\resumeProject
      { \href{https://github.com/addyhacke/MERN-Project-}{{\color{blue}Hospital Management System:}} } %Project Name
      {An online doctor appointment booking site.} %Project Name, Location Name
      {May, 2024} %Event Dates

      \resumeItemListStart
        \item {Tools \& technologies used: HTML, CSS, JavaScript, React, NodeJs, MySQL}
        \item {Implemented secure login mechanisms for users and administrators.}
        \item {Utilized JSON Web Tokens (JWTs) for session management and user validation.}
    \resumeItemListEnd

\vspace{-3mm}

\resumeProject
      { \href{https://github.com/addyhacke/netflix-login-page/}{{\color{blue}Netflix Login Page:}} } %Project Name
      {Improved understanding of front-end web development principles.} %Project Name, Location Name
      {Sept, 2023} %Event Dates

      \resumeItemListStart
        \item {Tools \& technologies used: HTML, CSS, JavaScript}
        \item {Enhanced skills in HTML5 and CSS3, focusing on modern web design techniques.}
    \resumeItemListEnd

\vspace{-4mm}

\section{\textbf{Achievements}}
\vspace{3.7mm}
\begin{itemize}[leftmargin=*, itemsep=8pt]
    \item \textbf{Leetcode:} Solved 250+ problems, aiming for 1000. Specializes in algorithms and data structures, ranks in top contests. [\href{https://leetcode.com/u/addy0328p/}{\color{blue}Profile}]
    
    \item \textbf{Google Cloud Skill Boost:} Completed program, earned 11 badges, top 1000 in Arcade Game program by GDSC IIIT Bhopal. [\href{https://www.cloudskillsboost.google/public_profiles/c56c4a79-dd72-406c-8810-c0ea84697193}{\color{blue}Profile}]
    
    \item \textbf{Ranked 3458:} Leetcode Contest 398
    
    \item \textbf{Team Lead:} Inspire Society, managed activities and initiatives.
\end{itemize}

%-------------------------------------------
\end{document}
